Research Journal

### 2018-07-05 journal/main.tex
More formatting

\entry{2018}{07}{02}
\subsection*{Infinite Dataset Test}
After much debugging to get the data generation during training working, we managed to run some experiments. Testing with infinite data did seem to improve generalization substantially compared to a simply larger dataset. So it seems that data is in fact a problem. We will somehow have to address this. 
\begin{figure}[H]
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[Typical embedding and similarity matrix of pairwise noise]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise3inf_plot.png}
            \label{fig:pairwise3inf_sub1}
        }
    \end{minipage}
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[Typical histogram for similarities of pairwise noise]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise3inf_hist.png}
            \label{fig:pairwise3inf_sub2}
        }
    \end{minipage}
    \centering
    \subfloat[Numerical results]{
        \begin{tabular}{|c|c|c|c|} \hline
                                       &    Trained Model        &    Previous Model        &    Baseline             \\ \hline
            Same Point Similarity      & 9.96e-01 $\pm$ 5.22e-03 & 9.97e-01 $\pm$ 4.16e-03 & 5.11e-01 $\pm$ 3.91e-01 \\ \hline
            Distinct Point Similarity  & 4.31e-01 $\pm$ 2.15e-01 & 6.34e-01 $\pm$ 1.29e-01 & 2.55e-01 $\pm$ 2.06e-01  \\ \hline
        \end{tabular}
        \label{fig:pairwise3inf_large_tab1}
    }
    \label{fig:pairwise3inf_plot}
\end{figure}
Despite this, the distinction between diagonal and off diagonal entries is not as sharp as I would like. I need to brainstorm ideas of how to handle that. There is some work on doing better selection for which edges in the averaging are relevant (e.g. Graph Attention Networks)

\entry{2018}{07}{03}
\subsection*{Infinite Dataset Test}
After much debugging to get the data generation during training working, we managed to run some experiments. Testing with infinite data did seem to improve generalization substantially compared to a simply larger dataset. So it seems that data is in fact a problem. We will somehow have to address this. 
\begin{figure}[H]
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[Typical embedding and similarity matrix of pairwise noise]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise5inf_plot.png}
            \label{fig:pairwise5inf_sub1}
        }
    \end{minipage}
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[For comparison, the non-infinite data trained version]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise5inf_plot_compare.png}
            \label{fig:pairwise5inf_sub2}
        }
    \end{minipage}
    \begin{minipage}{.9\linewidth}
        \centering
        \subfloat[Typical histogram for similarities of pairwise noise]{
            \includegraphics[width=0.5\textwidth]{figures/pairwise5inf_hist.png}
            \label{fig:pairwise5inf_sub3}
        }
    \end{minipage}
    \centering
    \subfloat[Numerical results]{
        \begin{tabular}{|c|c|c|c|} \hline
                                       &    Trained Model        &    Previous Model        &    Baseline             \\ \hline
            Same Point Similarity      & 9.97e-01 $\pm$ 3.70e-03 & 9.96e-01 $\pm$ 5.38e-03 & 5.11e-01 $\pm$ 3.91e-01 \\ \hline
            Distinct Point Similarity  & 6.71e-01 $\pm$ 1.55e-01 & 7.13e-01 $\pm$ 1.59e-01 & 2.55e-01 $\pm$ 2.06e-01  \\ \hline
        \end{tabular}
        \label{fig:pairwise5inf_tab1}
    }
    \label{fig:pairwise3inf_large_plot}
\end{figure}
It does OK, but this is still a fairly weak noise model. If the noise got more intense, we would need additional mechanisms to handle it. Hence the next mechanism.
\subsection*{Graph Attention Network Code Review}
I was looking at the aforementioned Graph Attention Network (GAT) \href{https://arxiv.org/pdf/1710.10903.pdf}{paper} and its \href{https://github.com/PetarV-/GAT}{code}.

\entry{2018}{07}{04}
\subsection*{GAT Implementation details}
After careful looking at the paper and the code for the GAT paper. After some confusing reading of the code, I figured out the way they are actually implementing it. It is more naive than I originally thought unfortunately. Let $E_k$ be the node embedding vectors at the current layer, with adjacency matrix $A$, and weight matrices $T_{k,1}, T_{k,2} \in \mathbb{R}^{n_k \times m_k}$, with $l$ being a point-wise non-linear function, and $s$ being the row-wise-softmax function:
\begin{align*}
f_1 =&\; E_k T_{k,1} \\
f_2 =&\; E_k T_{k,2} \\
Q_k =&\; l(f_1 So \mathbf{1}^\top + \mathbf{1} f_2^\top) \\
E_{k+1} =&\; \sigma \left( s(Q_k + A) E_k W_k \right)
\end{align*}
This has a few problems - This method is really dense. They have a sparse method but it computes this densely then makes it sparse. Also if you wanted to enforce the symmetry of the weights on the graph... there isn't really a simple way to do that. Except maybe doing something like using $Q_k' = (Q_k + Q_k^\top)/2$ which doesn't help the whole sparsity problem. There are some simple ways to make this sparse using for loops but I am uncertain how to do this using TensorFlow... or even PyTorch. However, as I don't see another way to learn the weights of the edges, this is what I'll be focusing on.

@@

\entry{2018}{07}{05}
\subsection*{Binary Cross Entropy}
Talking with others in the lab (Drew, Oleh) I realized instead of the L2 loss perhaps the Binary Cross Entropy Loss would perform better. Unfortunately this would make it less directly comparable to the optimization methods, but still I think it would worth trying. First I need to remove the

>>>>

\entry{2018}{07}{02}
\subsection*{Infinite Dataset Test}
After much debugging to get the data generation during training working, we managed to run some experiments.
Testing with infinite data did seem to improve generalization substantially compared to a simply larger dataset.
So it seems that data is in fact a problem, we will somehow have to address this. 
This is run on the pairwise dataset with $K=3$.
\begin{figure}[H]
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[Typical embedding and similarity matrix of pairwise noise]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise3inf_plot.png}
            \label{fig:pairwise3inf_sub1}
        }
    \end{minipage}
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[Typical histogram for similarities of pairwise noise]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise3inf_hist.png}
            \label{fig:pairwise3inf_sub2}
        }
    \end{minipage}
    \centering
    \subfloat[Numerical results]{
        \begin{tabular}{|c|c|c|c|} \hline
                                       &    Trained Model        &    Previous Model        &    Baseline             \\ \hline
            Same Point Similarity      & 9.96e-01 $\pm$ 5.22e-03 & 9.97e-01 $\pm$ 4.16e-03 & 5.11e-01 $\pm$ 3.91e-01 \\ \hline
            Distinct Point Similarity  & 4.31e-01 $\pm$ 2.15e-01 & 6.34e-01 $\pm$ 1.29e-01 & 2.55e-01 $\pm$ 2.06e-01  \\ \hline
        \end{tabular}
        \label{fig:pairwise3inf_large_tab1}
    }
    \label{fig:pairwise3inf_plot}
\end{figure}
Despite this, the distinction between diagonal and off diagonal entries is not as sharp as I would like.
I need to brainstorm ideas of how to handle that.
There is some work on doing better selection for which edges in the averaging are relevant (e.g. Graph Attention Networks)

\entry{2018}{07}{03}
\subsection*{Infinite Dataset Test}
I ran more experiments with the infinite dataset but with a harder dataset.
This is run on the pairwise dataset with $K=5$.
\begin{figure}[H]
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[Typical embedding and similarity matrix of pairwise noise]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise5inf_plot.png}
            \label{fig:pairwise5inf_sub1}
        }
    \end{minipage}
    \begin{minipage}{.45\linewidth}
        \centering
        \subfloat[For comparison, the non-infinite data trained version]{
            \includegraphics[width=0.9\textwidth]{figures/pairwise5inf_plot_compare.png}
            \label{fig:pairwise5inf_sub2}
        }
    \end{minipage}
    \begin{minipage}{.9\linewidth}
        \centering
        \subfloat[Typical histogram for similarities of pairwise noise]{
            \includegraphics[width=0.5\textwidth]{figures/pairwise5inf_hist.png}
            \label{fig:pairwise5inf_sub3}
        }
    \end{minipage}
    \centering
    \subfloat[Numerical results]{
        \begin{tabular}{|c|c|c|c|} \hline
                                       &    Trained Model        &    Previous Model        &    Baseline             \\ \hline
            Same Point Similarity      & 9.97e-01 $\pm$ 3.70e-03 & 9.96e-01 $\pm$ 5.38e-03 & 5.11e-01 $\pm$ 3.91e-01 \\ \hline
            Distinct Point Similarity  & 6.71e-01 $\pm$ 1.55e-01 & 7.13e-01 $\pm$ 1.59e-01 & 2.55e-01 $\pm$ 2.06e-01  \\ \hline
        \end{tabular}
        \label{fig:pairwise5inf_tab1}
    }
    \label{fig:pairwise3inf_large_plot}
\end{figure}
It does OK, but this is still a fairly weak noise model even with the stronger noise.
If the noise got more intense, we would need additional mechanisms to handle it.
Hence the next mechanism.

\subsection*{Graph Attention Network Code Review}
I was looking at the aforementioned Graph Attention Network (GAT) \href{https://arxiv.org/pdf/1710.10903.pdf}{paper} and its \href{https://github.com/PetarV-/GAT}{code}.

\entry{2018}{07}{04}
\subsection*{GAT Implementation details}
After careful looking at the paper and the code for the GAT paper.
After some confusing reading of the code, I figured out the way they are actually implementing it.
It is more naive than I originally thought unfortunately.
Let $E_k$ be the node embedding vectors at the current layer, with adjacency matrix $A$, and weight matrices $T_{k,1}, T_{k,2} \in \mathbb{R}^{n_k \times m_k}$, with $l$ being a point-wise non-linear function, and $s$ being the row-wise-softmax function:
\begin{align*}
f_1 =&\; E_k T_{k,1} \\
f_2 =&\; E_k T_{k,2} \\
Q_k =&\; l(f_1 So \mathbf{1}^\top + \mathbf{1} f_2^\top) \\
E_{k+1} =&\; \sigma \left( s(Q_k + A) E_k W_k \right)
\end{align*}
This has a few problems - This method is really dense.
They have a sparse method but it computes this densely then makes it sparse.
Also if you wanted to enforce the symmetry of the weights on the graph.
. there isn't really a simple way to do that.
Except maybe doing something like using $Q_k' = (Q_k + Q_k^\top)/2$ which doesn't help the whole sparsity problem.
There are some simple ways to make this sparse using for loops but I am uncertain how to do this using TensorFlow... or even PyTorch.
However, as I don't see another way to learn the weights of the edges, this is what I'll be focusing on.

@@

\entry{2018}{07}{05}
\subsection*{Binary Cross Entropy}
Talking with others in the lab (Drew, Oleh) I realized instead of the L2 loss perhaps the Binary Cross Entropy (BCE) Loss would perform better.
Unfortunately this would make it less directly comparable to the optimization methods, but still I think it would worth trying.
First I need to change the datasets to make sure that they don't go over weight 1, which means regeneration of all the datasets.
Next I have to add an addtional loss option for choosing between L2 loss and BCE loss.
